
---
params:
  date1: NA
  rptnotes: NA
  reportmap: NA
  netable: NA
  egreport: NA
  dmanamesexpsent: NA
  ftypesent: NA
  webshotpath: NA
output:
  html_document


---

<style type="text/css">

body, p, div, span, table, th, td {
  font-family: "Times New Roman", Times, serif !important;
}

h1, h2, h3, h4, h5, h6 {
  font-family: "Times New Roman", Times, serif !important;
}

caption {
  font-family: "Times New Roman", Times, serif !important;
  text-align: center !important;
  caption-side: top;
}

table {
  margin-bottom: 25px;
}

</style>
<h1 style="text-align:center; font-family:'Times New Roman', Times, serif; font-size:38px;">
NOAA Northeast Region<br>
Right Whale Aerial Survey Report
</h1>

<center><h1>`r params$date1`</h1></center>

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```
```{r echo = FALSE, warning = FALSE, results = 'asis', out.width = '80%', fig.align="center"}
knitr::include_graphics(params$webshotpath)
```

<center>`r params$rptnotes`</center>
\vspace*{-7mm}
<center>`r params$dmanamesexpsent`</center>
\vspace*{-7mm}
<center>`r params$ftypesent`</center>
\vspace*{-4mm}
```{r echo = FALSE, warning = FALSE, results = 'asis'}
knitr::kable(params$netable, caption = "Table 1:  Species Sighted") %>%
  kableExtra::kable_classic(full_width = FALSE)
```

```{r echo = FALSE, warning = FALSE, results = 'asis'}
knitr::kable(params$egreport, caption = "Table 2:  Right Whale Sighting(s) Details") %>%
 kableExtra::kable_classic(full_width = FALSE)
```
